Implementing Real-time Transport Services over an Ossified Network

### 2016-05-16 paper.tex
Finish sketching out Innovation and Ossification

We identify a number of places where TCP can evolve with comparative
freedom. 
Firstly, the TCP congestion control algorithm is executed by the end
points, and can be changed provided the new version requires no new
information to be exchanged. 
\todo{expand, and discuss how this evolution has occurred to date}

Then, we note that the API that is exposed to applications using TCP is
not visible to the network. 
- traditional API is restrictive, but flexibility to do out-of-order 
  delivery to applications

- easy to perform consistent segmentation on sending, and add COBS framing, 
  to get message-oriented semantics

- segments need be sent with contiguous sequence number space, resending
  segments to fill gaps in sequence number space caused by packet loss

Main issue with adding what we need is reliability. 
Leads to the question: can we work-around TCP reliability?

>>>>

We identify a number of places where TCP can evolve with comparative
freedom. These include congestion control, the end-point API, and data
segmentation. If care is taken, there is also the possibility to change
the reliability semantic.

The TCP congestion control algorithm is executed by the end points, and 
can be changed, provided the new version requires no new information to 
be exchanged. 
\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than the traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.

The API that is exposed to applications using TCP is not visible to the
network, and can be changed. 
\todo{discuss how the API can be relaxed to allow out-of-order delivery}
\todo{discuss how the API can be modified to accept/delivery a sequence
      of messages, rather than a byte stream, and how with consistent
      segmentation at the sender and COBS framing, this can be efficient}

These changes could address many of the transport service needs we have for
real-time applications, but still leave a critical issue of how to improve
timing behaviour. Specifically, how to enable partial reliability for TCP,
after which it is possible to layer-on support for managing deadlines and 
dependencies.
